Descriptive characteristics of Long COVID cohrots, matched

### 2022-11-15 characterisation/Code/Comparing_symptoms.Rmd
update

```{r include=FALSE}
# packages
library(SqlRender)
library(DBI)
library(DatabaseConnector)
library(here)
library(dplyr)
library(tidyr)
library(CDMConnector)
library(stringr)
library(lubridate)
library(gtsummary)
library(tableone)
library(kableExtra)
library(ggplot2)
library(forcats)

# Connection details ----
server    <- Sys.getenv("SERVER_JUN22")
server_dbi<- Sys.getenv("SERVER_DBI_JUN22")
user      <- Sys.getenv("DB_USER_JUN22")
password  <- Sys.getenv("DB_PASSWORD_JUN22")
port      <- Sys.getenv("DB_PORT_JUN22") 
host      <- Sys.getenv("DB_HOST_JUN22")

db <- dbConnect(RPostgres::Postgres(), 
                dbname = server_dbi,
                port = port,
                host = host, 
                user = user, 
                password = password)

targetDialect              <- "postgresql"
cdm_database_schema        <- "omop21t4_cmbd" 
vocabulary_database_schema <-"omop21t4_cmbd" 
write_schema               <-"results21t4_cmbd"

# Generate cdm object to access the tables
cdm <- cdm_from_con(db, 
             cdm_schema = cdm_database_schema,
             write_schema = write_schema,
             cohort_tables = c("er_long_covid_final_cohorts",
                               "er_long_covid_all_symptoms_cohorts"))

#  get ids for cohorts

cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
                          mutate(name= paste(sub(".*LongCov-ER_", "", name)))

@@

summary.characteristics <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table1.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 1,
  printToggle=FALSE)

@@

kable(summary.characteristics, 
      col.names = c("COVID-19 infection",  
                    "Long COVID-19, 90 days",
                    "SMD"
                    ))%>%
  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
 # pack_rows("Baseline comorbidities", 40, 44)

@@

summary.characteristics.negative <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table2.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 1,
  printToggle=FALSE)

@@

kable(summary.characteristics.negative, 
      col.names = c("Tested negative, earliest",  
                    "Long COVID-19 symptoms, 90 days",
                    "SMD"
                    ))%>%
  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
 # pack_rows("Baseline comorbidities", 40, 44)

@@

summary.characteristics.infection.negative <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table3.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 1,
  printToggle=FALSE)

@@

kable(summary.characteristics.infection.negative, 
      col.names = c("COVID-19 infection",  
                    "Tested negative, earliest",
                    "Tested negative, all events",
                    "SMD"
                    ))%>%
  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
 # pack_rows("Baseline comorbidities", 40, 44)

>>>>

```{r include=FALSE}
# packages
if (!require("pacman")) install.packages("pacman")
library(pacman)

p_load(SqlRender,
       DBI,
       here,
       tidyr,
       dplyr,
       dbplyr,
       CDMConnector,
       stringr,
       lubridate,
       tableone,
       kableExtra,
       ggplot2,
       forcats,
       gtsummary)

# Connection details ----
source("Code_to_Run.R", local = knitr::knit_global())
# Generate cdm object to access the tables
cdm <- cdm_from_con(db, 
             cdm_schema = cdm_database_schema,
             write_schema = write_schema,
             cohort_tables = c("er_long_covid_final_cohorts",
                               "er_long_covid_all_symptoms_cohorts"))

#  get ids for cohorts
cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
                          mutate(name= paste(sub(".*LongCov-ER_", "", name)))

@@

summary.characteristics <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table1.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)

@@

kable(summary.characteristics, 
      col.names = c("COVID-19 infection",  
                    "Long COVID-19, 90 days",
                    "SMD"
                    ))%>%
  kable_styling(bootstrap_options = c("striped", "bordered"))

@@

summary.characteristics.negative <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table2.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)

@@

kable(summary.characteristics.negative, 
      col.names = c("Tested negative, earliest",  
                    "Long COVID-19 symptoms, 90 days",
                    "SMD"
                    ))%>%
  kable_styling(bootstrap_options = c("striped", "bordered"))

@@

summary.characteristics.infection.negative <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table3.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)

@@

kable(summary.characteristics.infection.negative, 
      col.names = c("COVID-19 infection",  
                    "Tested negative, earliest",
                    "Tested negative, all events",
                    "SMD"
                    ))%>%
  kable_styling(bootstrap_options = c("striped", "bordered"))

### 2022-11-15 characterisation/Code/Comparing_symptoms_matched.Rmd
update

---
title: "Descriptive characteristics, matched"
output: html_document
---
---
title: "Descriptive characteristics of Long COVID Cohorts"
output: html_document
---

@@

```{r include=FALSE}
# packages
library(SqlRender)
library(DBI)
library(DatabaseConnector)
library(here)
library(dplyr)
library(tidyr)
library(CDMConnector)
library(stringr)
library(lubridate)
library(gtsummary)
library(tableone)
library(kableExtra)
library(ggplot2)
library(forcats)
library(tsibble)
library(MatchIt)
library(survey)

# get data for table 1
filtering_date <- as.Date("2020-09-01", "%Y-%m-%d")
load(here("data", "table1_data.Rdata"))
load(here("data", "table1_data_matched.Rdata"))

@@

# Baseline characteristics 
```{r}
table1.data<-rbind(  
# those without missing values
       table1_data_new_infections   %>%
        mutate(group = "1 COVID-19 infection"),
      table1_data_confirmed_infection  %>%
        mutate(group = "2 Confirmed infection"),
      table1_data_first_infection %>%
        mutate(group = "3 First infection"),
       table1_data_reinfections  %>%
        mutate(group = "4 Reinfections"),
        table1_data_tested_negative_earliest  %>%
        mutate(group = "5 Tested negative, earliest"),
      table1_data_tested_negative_all %>%
        mutate(group = "6 Tested negative, all "),
        table1_data_pcr_negative_earliest  %>%
        mutate(group = "7 PCR negative, earliest "),
         table1_data_pcr_negative_all  %>%
        mutate(group = "8 PCR negative, all ")) %>%
  filter(cohort_start_date >=filtering_date)

summary.characteristics <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table1.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=F,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics_covid_negative <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

@@

kable(summary.characteristics_covid_negative)%>%
  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
 # pack_rows("Baseline comorbidities", 40, 44)

@@

summary.characteristics.confirmed<-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics.reinfections<-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)
```

>>>>

---
title: "Descriptive characteristics of Long COVID cohrots, matched"
output: html_document
---

@@

```{r include=FALSE}
# packages
library(here)
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(gtsummary)
library(tableone)
library(kableExtra)
library(ggplot2)
library(forcats)
library(tsibble)
library(survey)

# get data for table 1
# get full testing_start from Code to Run
# source("Code_to_Run.R", local = knitr::knit_global())
full_testing_start_date <- as.Date("2020-09-01", "%Y-%m-%d")

load(here("data", "table1_data.Rdata"))
load(here("data", "table1_data_matched.Rdata"))

@@

# Baseline characteristics 
```{r}
table1.data<-rbind(  
# those without missing values
       table1_data_new_infections   %>%
        mutate(group = "1 COVID-19 infection"),
       table1_data_confirmed_infection  %>%
        mutate(group = "2 Confirmed infection"),
       table1_data_first_infection %>%
        mutate(group = "3 First infection"),
       table1_data_reinfections  %>%
        mutate(group = "4 Reinfections"),
        table1_data_tested_negative_earliest  %>%
        mutate(group = "5 Tested negative, earliest"),
       table1_data_tested_negative_all %>%
        mutate(group = "6 Tested negative, all "),
       table1_data_pcr_negative_earliest  %>%
        mutate(group = "7 PCR negative, earliest "),
       table1_data_pcr_negative_all  %>%
        mutate(group = "8 PCR negative, all ")) %>%
  filter(cohort_start_date >=full_testing_start_date)

summary.characteristics <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table1.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=F,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics_covid_negative <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  catDigits = 0,
  contDigits = 0,
  printToggle=FALSE)

@@

kable(summary.characteristics_covid_negative)%>%
  kable_styling(bootstrap_options = c("striped", "bordered"))

@@

summary.characteristics.confirmed<-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics.reinfections<-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
   catDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)
```
